---
title: "Election in Sweden"
author: "SILA KILICOGLU (silki753@student.liu.se) and SAMI FURKAN YILDIRIM (samyi572@student.liu.se)"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Election in Sweden}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## **Description**
The package provides data sets on various election results by municipalities in Sweden (Stockholm, Uppsala, Malmö, Göthenburg). The data was called from [Kolada](https://www.kolada.se/) with using web API.

## **Import**
```{r setup}
library(httr)
library(jsonlite)
library(election)
```
## **Arguments**
_city_name_
: A manucipality in Sweden. ("Stockholm", "Uppsala", "Malmo", "Gothenburg")  

## **Methods**
* _participation_rate()_
: This function returns a data set,which is about the percentage of voter turnout in the last parliamentary election for every 4 years in between 1998 to 2022, according to a city in Sweden. (Kpi: N05403)

* _political_party()_
: This function returns a data set,which is about the percentage of votes for the various political party in the last parliamentary election for every 4 years in between 2014 to 2022, according to a city in Sweden. (Kpi: N65841-N65849 respectively; Center Party, Christian Democrats, Liberals, Green Party, Moderates, Social Democrats, Sweden Democrats, Left Party, Other Parties)

* _first_vote()_
: This function returns a data set,which is about the percentage of first-time voters who voted in the last election to the Riksdag in 2018 and 2022, according to a city in Sweden. (Kpi: U17410)

***********************
## An Example of Usage

1. Create an instance of the _election_ reference class. Here the argument is taken as "Stockholm".

```r
el <- election("Stockholm")
```

2. For using participation_rate function:

```r
el$participation_rate()
```

3. For using political_party function:

```r
el$political_party()
```

4. For using first_vote function:

```r
el$first_vote()
```